|

### 2021-03-13 appendix/appendix.Rmd
not display r code appendix

[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Getulio Vargas Foundation, Brazil, <huzeyfealptekin@gmail.com>.

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

[^roman]: Research Associate, School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil, <catarinamroman@gmail.com>.

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

@@

The first step in our systematic review consisted in gathering a study sample. We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature. This search produced a database with many entries that were unrelated to our subject of investigation. To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is a seminal contribution to the field. Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.

@@

1. Matched treatment variable:
  + *N*: Number Legislators in the Lower House
  + *logN*: Log Number Legislators in the Lower House
  + *K*: Number Legislators in the Upper House

2. Matched outcome variable:
  + *ExpPC*: Expenditure Per Capita
  + *logExpPC*: Log Expenditure Per Capita
  + *PCTGDP*: Percent GDP Public Expenditure

@@

For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the _law of 1/n_.

```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", cache=TRUE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

Our sample differs considerably in regards to research design. One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was built with majoritarian systems in mind, to non-majoritarian democracies. In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated. The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", cache=TRUE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", cache=TRUE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "Dependent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients") +
  theme_bw()
```

@@

```{r, cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors") +
  theme_bw()
```

@@

One simple statistic that we can compute to assess the validity of the _law of 1/n_ is the frequency of positive and negative estimates in the study sample. Below we plot the frequency for all the papers included in the meta-analytic dataset.

```{r, fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

```{r, warning=F,message=F, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

@@

The _law of 1/n_ posits that we should expect a positive influence of legislature size on public expenditures. A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations. In statistical terms, consider a random variable representing the coefficient sign for the papers. As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the  chance of a positive sign. The _law of 1/n_ can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory. The null hypothesis for such a test is that:

@@

As we are taking an agnostic approach, we acknowledge that either the _law of 1/n_ ($p>0.5$), or the _reverse law of 1/n_ ($p<0.5$) could be true. In this case, the alternative hypothesis is $p\neq 0.5$. To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

In this paper, we use the random effects model. The empirical papers testing the _law of 1/n_ are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

\[
T_i \ = \ \theta_i + \varepsilon_i
\]

@@

\[
T_i \ = \ \mu + \xi_i + \varepsilon_i
\]

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
```

@@

The _law of 1/n_ was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=TRUE}
build_forest_het(mod, capt = NULL, hetvar = aux$elecsys2)
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F}
f2 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure Per Capita')
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
f3 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Log Expenditure Per Capita')
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
f4  <- build_forest(mod, NULL, 15, ttl = 'Log of Lower House Size\nand Log of Expenditure Per Capita')
```

@@

1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

```{r, cache=TRUE}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
f5 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Expenditure as Percentage of GDP')
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
f6 <- build_forest(mod, NULL, 15, ttl = 'Log Lower House Size\nand Expenditure as Percentage of GDP')
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
f7 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure as Percentage of GDP')
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by regression methods",warning=FALSE, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x N (RDD only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods",warning=FALSE, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, echo=T, warning=F, cache=TRUE}
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
```

@@

```{r, echo=T, warning=F, cache=TRUE}
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```

@@

```{r, warning=F, cache=T}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

@@

The _law of 1/n_ was formulated to analyse the budgetary allocation in majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.

```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=T}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

@@

```{r, warning=F, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=9, fig.height=8, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

@@

```{r, cache=T}
permutest(mod, progbar = F)
```

>>>>

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

@@

The first step in our systematic review consisted in gathering a study sample. We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature. This search produced a database with many entries that were unrelated to our subject of investigation. To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "*The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics*", which is a seminal contribution to the field. Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.

@@

1.  Matched treatment variable:

-   *N*: Number Legislators in the Lower House
-   *logN*: Log Number Legislators in the Lower House
-   *K*: Number Legislators in the Upper House

2.  Matched outcome variable:

-   *ExpPC*: Expenditure Per Capita
-   *logExpPC*: Log Expenditure Per Capita
-   *PCTGDP*: Percent GDP Public Expenditure

If a paper did not use a combination of these variables, we excluded it from the meta-analysis.

@@

For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.

```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE, size="footnotesize", echo = FALSE}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

Our sample differs considerably in regards to research design. One remarkable difference is that several authors apply the logics of the *law of 1/n*, which was built with majoritarian systems in mind, to non-majoritarian democracies. In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated. The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "Dependent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients") +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors") +
  theme_bw()
```

@@

One simple statistic that we can compute to assess the validity of the *law of 1/n* is the frequency of positive and negative estimates in the study sample. Below we plot the frequency for all the papers included in the meta-analytic dataset.

```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE, echo = FALSE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

```{r, size="footnotesize", warning=F, message=F, echo = FALSE, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

@@

The *law of 1/n* posits that we should expect a positive influence of legislature size on public expenditures. A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations. In statistical terms, consider a random variable representing the coefficient sign for the papers. As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the chance of a positive sign. The *law of 1/n* can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory. The null hypothesis for such a test is that:

@@

As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) could be true. In this case, the alternative hypothesis is $p\neq 0.5$. To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

In this paper, we use the random effects model. The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

$$
T_i \ = \ \theta_i + \varepsilon_i
$$

@@

$$
T_i \ = \ \mu + \xi_i + \varepsilon_i
$$

@@

```{r, cache=TRUE, echo = FALSE, size="footnotesize"}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r,include=F, warning=F, cache=TRUE, echo = FALSE}
f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
```

@@

The *law of 1/n* was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(mod, capt = NULL, hetvar = aux$elecsys2)
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)", warning=FALSE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, include=FALSE, warning=FALSE, echo = FALSE}
f2 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure Per Capita')
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, echo = FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
f3 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Log Expenditure Per Capita')
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
f4  <- build_forest(mod, NULL, 15, ttl = 'Log of Lower House Size\nand Log of Expenditure Per Capita')
```

@@

1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, echo = FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r, include=F, warning=F, echo = FALSE, cache=TRUE}
f5 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Expenditure as Percentage of GDP')
```

@@

```{r, echo = FALSE, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

@@

```{r, echo = FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
f6 <- build_forest(mod, NULL, 15, ttl = 'Log Lower House Size\nand Expenditure as Percentage of GDP')
```

@@

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
f7 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure as Percentage of GDP')
```

@@

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- logExpPC x N (RDD only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
```

@@

```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

The *law of 1/n* was formulated to analyse the budgetary allocation in majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.

```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

@@

```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
# Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=9, fig.height=8, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

```{r, size="footnotesize", cache=T, echo = FALSE}
permutest(mod, progbar = F)
```
